---
author:
- name: 
  affiliation: 
  corresponding: 
  address: 
  email: 
  role:
shorttitle: "Child BOI"
output:
  papaja::apa6_docx: default
  papaja::apa6_pdf: default
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: no
mask: no
draft: no
documentclass: apa7
classoption: man
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(jtools)
library(stats)
library(Hmisc)
library(ggplot2)
library(olsrr)
library(corrplot)
library(renv)
library(papaja)
library(plyr)
library(dplyr)
library(magrittr)
library(readr)
library(apaTables)
library(tidyr)
library(interactions)
library(lm.beta)
library(ggplot2)
library(cowplot)
library(psych)
library(janitor)
library(ggcorrplot)
library(lme4)
```

# Results

The data were cleaned following methods laid out in Pexman et al. (2019) to screen for invalid responses (e.g., inattentive participants, bot responses) in the online questionnaire. First, 10 participants who indicated hearing less than 50% English at home were excluded. We then excluded three participants who completed less than 33% of the questionnaire and 32 participants who provided the same rating for more than 12 words in a row. Then ratings for the 20 control words were compared to ratings already acquired for those words from the pilot study. Any participant whose ratings correlated with the pilot data between -0.5 and 0.2 were to be excluded, however, all remaining participants had a correlation higher than 0.2 across the control words. Finally, we calculated the correlation between each remaining participants’ ratings and the average rating of all participants on the same words. Any participant with a correlation less than 0.10 was to be excluded, however no additional participants were removed due to this criterion. A total of 45 participants were removed via these data cleaning steps, leaving responses from 248 participants. Table 1 provides the difference in demographic information for the total and retained samples. Demographic features did not vary drastically between the full and retained samples. 

```{r include = FALSE}
#Add demographics table
```


```{r include = FALSE}
##Validity and reliability section
#read in data
CBOI_PC <- read_csv("CBOI_Prac_Control.csv")
CBOI_Pilot <- read_csv("Pilot_ratings.csv")

#Calculate split-half reliability
##Remove practice items and type column and transpose
CBOI_C <- CBOI_PC %>% 
  filter(Type == "Control") %>% 
  select(!Type) %>% 
  t() %>% 
  as.data.frame()

#Remove mean columns and transpose pilot data
CBOI_Pilot_t <- CBOI_Pilot %>% 
  select(!c(Mean, SD, N)) %>% 
  t() %>% 
  as.data.frame()

##Rename columns using first row and then remove first row
names(CBOI_C) <- CBOI_C %>% 
  slice(1) %>% 
  unlist()

names(CBOI_Pilot_t) <- CBOI_Pilot_t %>% 
  slice(1) %>% 
  unlist()

CBOI_C <- CBOI_C %>% 
  slice(-1) %>% 
  mutate_if(is.character, as.numeric)

CBOI_Pilot_t <- CBOI_Pilot_t %>% 
  slice(-1) %>% 
  mutate_if(is.character, as.numeric)

##Divide into two datasets, odd and even rows
evenCBOI <- CBOI_C %>% 
  filter(row_number() %% 2 == 0) 

oddCBOI <- CBOI_C %>% 
  filter(row_number() %% 2 == 1) 

evenCBOIPilot <- CBOI_Pilot_t %>% 
  filter(row_number() %% 2 == 0) 

oddCBOIPilot <- CBOI_Pilot_t %>% 
  filter(row_number() %% 2 == 1) %>% 
  filter(ache != "NA")

#Test correlation across all control items
data_long_odd <- gather(oddCBOI, factor_key = TRUE)
data_long_even <- gather(evenCBOI, factor_key = TRUE)
data_long_odd <- data_long_odd %>% 
  rename(Odd_Rate = value)
data_long_even <- data_long_even %>% 
  rename(Even_rate = value)
data_all <- data_long_odd
data_all$Even_rate <- data_long_even$Even_rate
shr_study <-cor(data_all$Odd_Rate, data_all$Even_rate, use = "complete.obs")

#Test correlation across all pilot items
data_long_oddp <- gather(oddCBOIPilot, factor_key = TRUE)
data_long_evenp <- gather(evenCBOIPilot, factor_key = TRUE)
data_long_oddp <- data_long_oddp %>% 
  rename(Odd_Rate = value)
data_long_evenp <- data_long_evenp %>% 
  rename(Even_rate = value)
data_allp <- data_long_oddp
data_allp$Even_rate <- data_long_evenp$Even_rate
shr_pilot <-cor(data_allp$Odd_Rate, data_allp$Even_rate, use = "complete.obs")

#Calculate ICC using function from psych package (model 2 two-way - each item assessed by each rater, raters randomly selected)
icc_data <- CBOI_PC %>% 
  filter(Type == "Control") %>% 
  select(!c(Type, Item))

icc_study <- psych::ICC(icc_data) 

#Calculate ICC using function from psych package on pilot data (model 2 two-way - each item assessed by each rater, raters randomly selected)
icc_data_pilot <- CBOI_Pilot %>% 
  select(!c(Mean, SD, N)) %>% 
  mutate_if(is.character, as.numeric)
  

icc_pilot <- psych::ICC(icc_data_pilot) 
```

```{r include = FALSE}
##Descriptive statistics and distributions of Child BOI ratings
#Calculate descriptive statistics for ratings data
CBOI <- read_csv("CBOI_mean_sd.csv")
POS <- read_csv("PoS_Information.csv")

CBOI <- CBOI %>% 
  filter(N < 200) %>% 
  rename("Child_BOI" = "Mean")
CBOI <- left_join(CBOI, POS, by = "Word")

desc_CBOI <-describe(CBOI$Child_BOI)
mean_CBOI <- round(mean(CBOI$Child_BOI), digits = 2)
median_CBOI <- round(median(CBOI$Child_BOI), digits = 2)
sd_CBOI <- round(sd(CBOI$Child_BOI), digits = 2)
min_CBOI <- round(min(CBOI$Child_BOI), digits = 2)
max_CBOI <- round(max(CBOI$Child_BOI), digits = 2)
q_CBOI <- quantile(CBOI$Child_BOI)

Statistic <- c("Mean", "Median", "Standard Deviation", "Minimum", "Maximum", "1st quartile", "3rd quartile", "Skewness", "Kurtosis")

Value <- c(mean_CBOI, median_CBOI, sd_CBOI, min_CBOI, max_CBOI, 2.63, 4.72, desc_CBOI$skew, desc_CBOI$kurtosis )

descriptives <- data.frame(Statistic, Value)

#Create histogram of all items
p1 <- ggplot(CBOI, aes(x = Child_BOI)) + geom_histogram(bins = 30, fill = "#808080", color = "#e9ecef") + theme_apa() + labs(x = "BOI Rating", y = "Count") + scale_y_continuous(expand = c(0,0))

#Create histogram of ratings by word type
PoS_plot <- CBOI %>% 
  filter(Dom_PoS %in% c("Noun", "Verb", "Adverb", "Adjective"))

p2 <- ggplot(PoS_plot, aes(x = Child_BOI, group = Dom_PoS, fill = Dom_PoS)) + geom_density(alpha = 0.5) + theme_apa() + xlab("BOI Rating") + ylab("Density") + labs(fill = "Word Type") + theme(legend.position = c(0.85, 0.7)) + coord_cartesian(xlim = c(1,7), ylim = c(0, 0.55), expand = FALSE)

```


```{r include = FALSE, message = FALSE}
##Relationship to other lexical semantic dimensions
#Import MCDI data
MCDI <- read_csv("MCDI.csv")
MCDI$MCDI_AoA <- as.numeric(MCDI$MCDI_AoA)

#Import test-based and ratings-based AoA
AoA <- read_csv("Dale_ORourke_AoA.csv")

#remove all columns but word and rating
AoA_test <- AoA %>% 
  select(Word, AoAtestbased)

AoA_rate <- AoA %>% 
  select(Word, AoArating)

#take min values for unique items in AoA test based norms
low_AoA_test <- aggregate(AoAtestbased ~ Word, AoA_test, min)
max_AoA_test <- aggregate(AoAtestbased ~ Word, AoA_test, max)
AoA_rate_unique <- unique(AoA_rate)
colnames(low_AoA_test) <- c("Word", "AoA_test_min")
colnames(max_AoA_test) <- c("Word", "AoA_test_max")

#merge unique AoA test-based min and max values with concreteness and AoA ratings to see availability
AoA_all <- merge(low_AoA_test, max_AoA_test)

#Import adult BOI
ABOI <- read_csv("Pexman_BOI_Norms.csv")

ABOI <- ABOI %>% 
  select(Word, Mean) %>% 
  rename(Adult_BOI = Mean)

#Import lexical values from ELP
ELP <- read_csv("ELP.csv")

#Import CHILDES frequency
Freq_CHILDES <- read_csv("Freq_CHILDES.csv")

#Import semantic richness variables
SemRich <- read_csv("SemanticRichness.csv")

SemVar <- SemRich %>% 
  select(Word, AoA_K, Conctreteness_B, SER_JY, Imageability_Cs, Valence_W, Arousal_W, SemD_H, Length, LgSUBTLWF, OLD, PLD, NoF_B)

#Combine data
CBOI <- left_join(CBOI, SemVar, by = "Word")
CBOI <- left_join(CBOI, AoA_all, by = "Word")
CBOI <- left_join(CBOI, ABOI, by = "Word")
CBOI <- left_join(CBOI, Freq_CHILDES, by = "Word")
CBOI <- left_join(CBOI, MCDI, by = "Word")

CBOI_corr <- CBOI %>% 
  select(SemD_H, NoF_B, Arousal_W, Valence_W, SER_JY, Imageability_Cs, Conctreteness_B, AoA_K, AoA_test_min, MCDI_AoA, PLD, OLD, LgSUBTLWF, lgFreq, Length, Adult_BOI, Child_BOI)%>%   
  rename("Child BOI" = "Child_BOI", "Adult BOI" = "Adult_BOI", "AoA - rating" = "AoA_K", "Concreteness" = "Conctreteness_B", "SER" = "SER_JY", "Imageability" = "Imageability_Cs", "Valence" = "Valence_W", "Arousal" = "Arousal_W", "Semantic Diversity" = "SemD_H", "log subtitle Frequency" = "LgSUBTLWF", "log CHILDES Frequency" = "lgFreq", "Number of Features" = "NoF_B", "AoA - Test-based" = "AoA_test_min", "AoA - MCDI" = "MCDI_AoA")

corr_results <- round(cor(CBOI_corr, use = "pairwise.complete.obs"),2)

p3 <- ggcorrplot(corr_results, type = "upper", lab = TRUE, outline.col = "white", ggtheme = ggplot2::theme_minimal, colors = c("#6bd4ae", "white", "#7a6bd4"))

all_CBOI <- left_join(CBOI, CBOI_Pilot, by = "Word")

all_CBOI <- all_CBOI %>% 
  select(Word, Child_BOI, Adult_BOI, Mean)

CBOI_corrs <- cor(all_CBOI$Child_BOI, all_CBOI$Mean, use = "complete.obs")
CBOI_ABOI_corrs <- cor(all_CBOI$Child_BOI, all_CBOI$Adult_BOI, use = "complete.obs")
```


```{r include = FALSE, message = FALSE}
##Relationship between Child and Adult BOI
#Create dataframe with only words, Child and Adult BOI
CA_BOI_Plot <- CBOI %>% 
  select(Word, Child_BOI, Adult_BOI) %>% 
  mutate(Diff = Child_BOI - Adult_BOI) %>% 
  mutate(Diff_type = case_when(Diff >= 2.82 ~ "Child High", Diff <= -2.82 ~ "Child Low", Diff > -2.82 | Diff < 2.82 ~ "No Diff")) %>% 
  drop_na(Diff_type) 

p4 <- ggplot(CA_BOI_Plot, aes(x = Child_BOI, y = Adult_BOI, label = Word)) + geom_point(aes(color = Diff_type), alpha = 0.75) + geom_smooth(method = lm) + geom_text(aes(label=ifelse(Word == "cigar" | Word == "gun" | Word == "typewriter" | Word == "engineer" | Word == "blue" | Word == "ouch" | Word == "birthday" | Word == "excitement", as.character(Word),"")), hjust = 0, vjust = 0, size = 4) + theme_apa() + theme(legend.position = "none") + xlab("Child BOI Rating") + ylab("Adult BOI Rating") + scale_color_brewer(palette = "Set2")

```

The resulting child BOI ratings are available at: LINK. Descriptive statistics for child BOI ratings on 3,384 words are presented in Table 2. Child BOI ratings were normally distributed (Figure 1), with a some suggestion of a bi-modal distribution. A kernel density plot of Child BOI ratings by syntactic class shows that the words in the higher end of the ratings distribution tend to be nouns, whereas the ratings peak in the lower half of the scale appears to represent ratings for adjectives, adverbs, and verbs (Figure 2).


```{r table 1 and plots 1 and 2, echo=FALSE, fig.height = 4.5, fig.width = 7, echo = FALSE, message = FALSE}
#Create table of descriptive statistics
apa_table(descriptives, caption = table1$table.title, note = "Descriptive Statistics of Child BOI Ratings (N = 3,384)", row.names = FALSE)

p1
p2
```

We examined the reliability of the ratings by computing split half reliability for the 20 control words that each participant rated (splitting the participants into two groups by taking every other participant and calculating the correlation between ratings on the control items between the two groups). The split-half reliability indicated moderate reliability, *r* = `r shr_study`. We also computed the intraclass correlation coefficient (ICC) on control word ratings from all participants, with an ICC of `r round(icc_study$results[2,2], digits = 2)` indicating moderate reliability. We then examined the validity of the ratings by comparing the Child BOI ratings to Child BOI ratings collected in the pilot study, as well as to the adult BOI ratings reported in Pexman et al. (2019). The current child BOI ratings were strongly correlated with the ratings collected in the pilot study (*r* = `r round(CBOI_corrs, digits = 2)`) and moderately correlated with the adult BOI ratings (*r* = `r round(CBOI_ABOI_corrs, digits = 2)`). An examination of the items which differed in child vs adult BOI ratings revealed that there were some terms with higher adult BOI ratings (e.g., cigar, gun, engineer) and some words with higher child BOI ratings (e.g., color words like yellow, red, blue, etc., birthday, ouch; see Figure 3).

```{r fig.height = 7, fig.width = 11, echo = FALSE, message = FALSE}
##Show scatterplot
p4 
```

We then examined correlations between the new Child BOI ratings and other lexical and semantic dimensions, including length (number of letters), log frequency derived from child-directed speech in the CHILDES databases (MacWhinney, 2000), orthographic and phonological Levenshtein distance (CITE), age-of-acquisition derived from the MacArthur Bates Communicative Development Inventory (MCDI; Fenson et al., 1993), a test-based measure of age-of-acquisition derived from Dale and O'Rourke (1981) and updated by Brysbaert and Biemiller (2017), a ratings-based measure of age-of-acquisition (Kuperman et al., 2012), concreteness (Brysbaert et al., 2012), imageability (Juhasz et al.), sensory experience ratings (Juhasz et al.), valence (Warriner et al., 2013), arousal (Warriner et al., 2013), and number of features (Buchanan et al.,). The correlations are presented in Figure 4.

Child BOI was strongly related to number of features (*r* = `r corr_results[16,2]`), sensory experience ratings (*r* = `r corr_results[16,5]`), imageability (*r* = `r corr_results[16,6]`), concreteness (*r* = `r corr_results[16,7]`), and log frequency in child directed speech (*r* = `r corr_results[16,13]`). Child BOI was also strongly related to all three measures of AoA (*r* = `r corr_results[16,10]` for MCDI, *r* = `r corr_results[16,9]` for test-based, and *r* = `r corr_results[16,8]` for ratings-based), unlike adult BOI which was only correlated with the AoA measure derived from the MCDI. Child BOI is more strongly related to SER than Adult BOI and frequency in child-direct speech, whereas Adult BOI is more strongly related to semantic diversity, imageability, and concreteness.

```{r fig.height = 10, fig.width = 10, echo = FALSE, message = FALSE}
##Show corrplot
p3

```

The relationships between child and adult BOI to AoA were tested using hierarchical multiple regression. Each regression included log frequency in child-directed speech, length, and imageability in the first step, after which either child or adult BOI was entered as a predictor in step 2. For each measure of AoA, only words that had ratings for both child and adult BOI were included in the analyses in order to provide a fair comparison between the two predictors. The regression model predicting MCDI AoA included 404 items and the regression models for test-based and ratings-based AoA included 1,925 items.
	
```{r MCDI Model, include = FALSE}
library(reghelper)
library(lmSupport)

MCDIdat <- CBOI %>% 
  select(Word, lgFreq, Length, Imageability_Cs, Child_BOI, Adult_BOI, MCDI_AoA) %>% 
  drop_na()

MCDI_step1 <- lm(MCDI_AoA ~ lgFreq + Length + Imageability_Cs, data = MCDIdat)
MCDI_adultmodel <- lm(MCDI_AoA ~ lgFreq + Length + Imageability_Cs + Adult_BOI, data = MCDIdat)
MCDI_childmodel <- lm(MCDI_AoA ~ lgFreq + Length + Imageability_Cs + Child_BOI, data = MCDIdat)

summary(MCDI_adultmodel)
summary(MCDI_childmodel)
summary(MCDI_step1)

#Make Variables column for table
variables <- c("Intercept", "log CHILDES Frequency", "Length", "Imageability", "BOI")

#Make Adult Columns
adult_MCDI_beta <-round(beta(MCDI_adultmodel)$coefficients[,1], digits = 2)
adult_MCDI_se <-round(beta(MCDI_adultmodel)$coefficients[,2], digits = 2)
adult_MCDI_t <-round(beta(MCDI_adultmodel)$coefficients[,3], digits = 2)
adult_MCDI_p <-round(beta(MCDI_adultmodel)$coefficients[,4], digits = 3)
adult_MCDI_R2 <- round(c(summary(MCDI_adultmodel)$adj.r.squared, 0, 0, 0, 0), digits = 4)
adult_MCDI_delta <- round(c(modelCompare(MCDI_step1, MCDI_adultmodel)$Delta, 0, 0, 0, 0), digits = 4)

child_MCDI_beta <-round(beta(MCDI_childmodel)$coefficients[,1], digits = 2)
child_MCDI_se <-round(beta(MCDI_childmodel)$coefficients[,2], digits = 2)
child_MCDI_t <-round(beta(MCDI_childmodel)$coefficients[,3], digits = 2)
child_MCDI_p <-round(beta(MCDI_childmodel)$coefficients[,4], digits = 3)
child_MCDI_R2 <- round(c(summary(MCDI_childmodel)$adj.r.squared, 0, 0, 0, 0), digits = 4)
child_MCDI_delta <- round(c(modelCompare(MCDI_step1, MCDI_childmodel)$Delta, 0, 0, 0, 0), digits = 4)

#Make Table
table2 <- data.frame(variables, adult_MCDI_beta, adult_MCDI_se, adult_MCDI_t, adult_MCDI_p, adult_MCDI_R2, adult_MCDI_delta, child_MCDI_beta, child_MCDI_se, child_MCDI_t, child_MCDI_p, child_MCDI_R2, child_MCDI_delta)

```

**MCDI**
The predictors log CHILDES frequency, length, and imageability entered in the first stage accounted for `r sprintf("%0.2f%%", summary(MCDI_step1)$adj.r.squared * 100)` of variance in MCDI AoA. The addition of adult BOI ratings to the model accounted for an additional `r sprintf("%0.2f%%", (summary(MCDI_adultmodel)$adj.r.squared - summary(MCDI_step1)$adj.r.squared) * 100)` of variance, whereas the addition of child BOI ratings to the model accounted for an additional `r sprintf("%0.2f%%", (summary(MCDI_childmodel)$adj.r.squared - summary(MCDI_step1)$adj.r.squared) * 100)`. See Table 2 for estimates of all model parameters.


```{r show table 2, echo = FALSE, message = FALSE}
apa_table(table2, caption = "Check it out")
```

```{r AoA testbased Model, include = FALSE}
AoAtest_dat <- CBOI %>% 
  select(Word, lgFreq, Length, Imageability_Cs, Child_BOI, Adult_BOI, AoA_test_min) %>% 
  drop_na()

AoA_test_step1 <- lm(AoA_test_min ~ lgFreq + Length + Imageability_Cs, data = AoAtest_dat)
AoA_test_adultmodel <- lm(AoA_test_min ~ lgFreq + Length + Imageability_Cs + Adult_BOI, data = AoAtest_dat)
AoA_test_childmodel <- lm(AoA_test_min ~ lgFreq + Length + Imageability_Cs + Child_BOI, data = AoAtest_dat)

summary(AoA_test_adultmodel)
summary(AoA_test_childmodel)
summary(AoA_test_step1)

#Make Variables column for table
variables <- c("Intercept", "log CHILDES Frequency", "Length", "Imageability", "BOI")

#Make Adult Columns
adult_AoA_test_beta <-round(beta(AoA_test_adultmodel)$coefficients[,1], digits = 2)
adult_AoA_test_se <-round(beta(AoA_test_adultmodel)$coefficients[,2], digits = 2)
adult_AoA_test_t <-round(beta(AoA_test_adultmodel)$coefficients[,3], digits = 2)
adult_AoA_test_p <-round(beta(AoA_test_adultmodel)$coefficients[,4], digits = 3)
adult_AoA_test_R2 <- round(c(summary(AoA_test_adultmodel)$adj.r.squared, 0, 0, 0, 0), digits = 4)
adult_AoA_test_delta <- round(c(modelCompare(AoA_test_step1, AoA_test_adultmodel)$Delta, 0, 0, 0, 0), digits = 4)

child_AoA_test_beta <-round(beta(AoA_test_childmodel)$coefficients[,1], digits = 2)
child_AoA_test_se <-round(beta(AoA_test_childmodel)$coefficients[,2], digits = 2)
child_AoA_test_t <-round(beta(AoA_test_childmodel)$coefficients[,3], digits = 2)
child_AoA_test_p <-round(beta(AoA_test_childmodel)$coefficients[,4], digits = 3)
child_AoA_test_R2 <- round(c(summary(AoA_test_childmodel)$adj.r.squared, 0, 0, 0, 0), digits = 4)
child_AoA_test_delta <- round(c(modelCompare(AoA_test_step1, AoA_test_childmodel)$Delta, 0, 0, 0, 0), digits = 4)

#Make Table
table3 <- data.frame(variables, adult_AoA_test_beta, adult_AoA_test_se, adult_AoA_test_t, adult_AoA_test_p, adult_AoA_test_R2, adult_AoA_test_delta, child_AoA_test_beta, child_AoA_test_se, child_AoA_test_t, child_AoA_test_p, child_AoA_test_R2, child_AoA_test_delta)

```

**Test-based AoA**
The predictors log CHILDES frequency, length, and imageability entered in the first stage accounted for `r sprintf("%0.2f%%", summary(AoA_test_step1)$adj.r.squared * 100)` of variance in MCDI AoA. The addition of adult BOI ratings to the model accounted for an additional `r sprintf("%0.2f%%", (summary(AoA_test_adultmodel)$adj.r.squared - summary(AoA_test_step1)$adj.r.squared) * 100)` of variance, whereas the addition of child BOI ratings to the model accounted for an additional `r sprintf("%0.2f%%", (summary(AoA_test_childmodel)$adj.r.squared - summary(AoA_test_step1)$adj.r.squared) * 100)`. See Table 3 for estimates of all model parameters.

```{r show table 3, echo = FALSE, message = FALSE}
apa_table(table3, caption = "Check it out")
```

```{r AoA ratebased Model, include = FALSE}
AoArate_dat <- CBOI %>% 
  select(Word, lgFreq, Length, Imageability_Cs, Child_BOI, Adult_BOI, AoA_K) %>% 
  drop_na()

AoA_rate_step1 <- lm(AoA_K ~ lgFreq + Length + Imageability_Cs, data = AoArate_dat)
AoA_rate_adultmodel <- lm(AoA_K ~ lgFreq + Length + Imageability_Cs + Adult_BOI, data = AoArate_dat)
AoA_rate_childmodel <- lm(AoA_K ~ lgFreq + Length + Imageability_Cs + Child_BOI, data = AoArate_dat)

summary(AoA_rate_adultmodel)
summary(AoA_rate_childmodel)
summary(AoA_rate_step1)

#Make Variables column for table
variables <- c("Intercept", "log CHILDES Frequency", "Length", "Imageability", "BOI")

#Make Adult Columns
adult_AoA_rate_beta <-round(beta(AoA_rate_adultmodel)$coefficients[,1], digits = 2)
adult_AoA_rate_se <-round(beta(AoA_rate_adultmodel)$coefficients[,2], digits = 2)
adult_AoA_rate_t <-round(beta(AoA_rate_adultmodel)$coefficients[,3], digits = 2)
adult_AoA_rate_p <-round(beta(AoA_rate_adultmodel)$coefficients[,4], digits = 3)
adult_AoA_rate_R2 <- round(c(summary(AoA_rate_adultmodel)$adj.r.squared, 0, 0, 0, 0), digits = 4)
adult_AoA_rate_delta <- round(c(modelCompare(AoA_rate_step1, AoA_rate_adultmodel)$Delta, 0, 0, 0, 0), digits = 4)

child_AoA_rate_beta <-round(beta(AoA_rate_childmodel)$coefficients[,1], digits = 2)
child_AoA_rate_se <-round(beta(AoA_rate_childmodel)$coefficients[,2], digits = 2)
child_AoA_rate_t <-round(beta(AoA_rate_childmodel)$coefficients[,3], digits = 2)
child_AoA_rate_p <-round(beta(AoA_rate_childmodel)$coefficients[,4], digits = 3)
child_AoA_rate_R2 <- round(c(summary(AoA_rate_childmodel)$adj.r.squared, 0, 0, 0, 0), digits = 4)
child_AoA_rate_delta <- round(c(modelCompare(AoA_rate_step1, AoA_rate_childmodel)$Delta, 0, 0, 0, 0), digits = 4)

#Make Table
table4 <- data.frame(variables, adult_AoA_rate_beta, adult_AoA_rate_se, adult_AoA_rate_t, adult_AoA_rate_p, adult_AoA_rate_R2, adult_AoA_rate_delta, child_AoA_rate_beta, child_AoA_rate_se, child_AoA_rate_t, child_AoA_rate_p, child_AoA_rate_R2, child_AoA_rate_delta)

```

**Rating-based AoA**
The predictors log CHILDES frequency, length, and imageability entered in the first stage accounted for `r sprintf("%0.2f%%", summary(AoA_rate_step1)$adj.r.squared * 100)` of variance in MCDI AoA. The addition of adult BOI ratings to the model accounted for an additional `r sprintf("%0.2f%%", (summary(AoA_rate_adultmodel)$adj.r.squared - summary(AoA_rate_step1)$adj.r.squared) * 100)` of variance, whereas the addition of child BOI ratings to the model accounted for an additional `r sprintf("%0.2f%%", (summary(AoA_rate_childmodel)$adj.r.squared - summary(AoA_rate_step1)$adj.r.squared) * 100)`. See Table 4 for estimates of all model parameters.

```{r show table 4, echo = FALSE, message = FALSE}
apa_table(table4, caption = "Check it out")
```

